A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
Correct namings and back transformations for contrasts

```{r}
PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity - 1)/8) * 100
PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvSQ <- rma.mv(
   yi = yi_percent,
   V = vi_percent,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvSQ)
```
<br>  
<br>  
<br>

@@

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

contrast_Ssum[6:15,] %>%
   mutate(coefficients = -sqrt(abs(coefficients)),
          StdErr = sqrt(StdErr))%>%
   flextable()%>%
   autofit()
```

@@

`Recommended_plus` limited disease severity significantly better than any other spray treatment. 
`Late_plus` limited disease severity significantly better than a single `Late` application. 
This indicates that two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.

>>>>

```{r}
PM_dat_D$yi_percent <- log(((PM_dat_D$PM_final_severity - 1)/8) * 100 +1)
PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
hist(PM_dat_D$yi_percent)
summary(PM_dat_D$yi_percent)
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = yi_percent,
   V = vi_percent,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvPer)
```
Model does not converge we will proceed with the square transformed severity

@@

intercept <-PMsev_mvSQ$b[1,1]
z <- PMsev_mvSQ$zval[1]

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mvSQ, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

contrast_Ssum[6:15,] %>%
   mutate(coefficients = sqrt(coefficients + intercept) - sqrt(intercept),
          StdErr = sqrt(StdErr + intercept) - sqrt(intercept),
          Zvalue = sqrt(Zvalue + z) - sqrt(z))%>%
   flextable()%>%
   autofit()
```

@@

`Recommended_plus` limited disease severity significantly better than any other spray treatment. 
Early sprays were not effective in decreasing disease severity.
Two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.
